Mechanization of Separation in Generic Extensions

### 2019-01-10 LICS/isabelle.tex

The source code is written for the 2018 version of Isabelle and can be downloaded
from 
\ifIEEE
\begin{center}
\texttt{https://cs.famaf.unc.edu.ar/\~{}mpagano/forcing/}
\end{center}
\fi
\ifarXiv
\url{https://cs.famaf.unc.edu.ar/~mpagano/forcing/}
\fi
(with
minor modifications, it can be run in Isabelle2016-1). Most of it is
presented in the (nowadays standard) declarative flavour called
\emph{Isar} \cite{DBLP:conf/tphol/Wenzel99}, where intermediate
statements in the course of a proof are explicitly stated,
interspersed with automatic tactics handling more trivial steps. The
goal is that the resulting text, a \emph{proof document}, can be
understood without the need of re-playing it viewing the proof state
at each point.

>>>>

The source code is written for the 2018 version of Isabelle and can be downloaded
from 
\ifIEEE
\begin{center}
\texttt{https://cs.famaf.unc.edu.ar/\~{}mpagano/forcing/}
\end{center}
\fi
\ifarXiv
\url{https://cs.famaf.unc.edu.ar/~mpagano/forcing/}
\fi
(with
minor modifications, it can be run in Isabelle2016-1). Most of it is
presented in the (nowadays standard) declarative flavour called
\emph{Isar} \cite{DBLP:conf/tphol/Wenzel99}, where intermediate
statements in the course of a proof are explicitly stated,
interspersed with automatic tactics handling more trivial steps. The
goal is that the resulting text, a \emph{proof document}, can be
understood without the need of replaying it and viewing the proof state
at each point.
